### 2022-03-07 [2020-08]_ACMTOMS_(MQSI)/paper/mqsi20.tex
Working on revision. Added references to papers, making summaries. Initialized response document.

% Abstract and Introduction
{\rmVIII\parindent=0pt MQSI is a Fortran 2003 subroutine for constructing
monotone quintic spline interpolants to monotone data. Using sharp
theoretical monotonicity constraints, first and second derivative estimates
at data provided by a quadratic facet model are refined to produce a
$\scriptstyle C^2$ monotone interpolant.  Algorithm and implementation
details, complexity and sensitivity analyses, usage information, and a
brief performance study are included.

@@

@@

>>>>

% Abstract and Introduction
{\rmVIII\parindent=0pt MQSI is a Fortran 2003 subroutine for constructing
monotone quintic spline interpolants to univariate monotone data. Using sharp
theoretical monotonicity constraints, first and second derivative estimates
at data provided by a quadratic facet model are refined to produce a
univariate $\scriptstyle C^2$ monotone interpolant.  Algorithm and implementation
details, complexity and sensitivity analyses, usage information, a
brief performance study, and comparisons with other spline approaches are included.

@@

\bigskip\hrule\bigskip

@@

%% No extra knots, rational functions, sufficiency and necessity proven, works for unequally spaced data, no code associated with the paper, no algorithm provided for the initialization for free shape parameters.
\refj{Abbas M., Majid, A. A. and Ali, J. M.}{2012}{Monotonicity-preserving $C^2$ rational cubic spline for monotone data}{Applied Mathematics and Computation}{219(6):2885--2895}

%% 
\refj{Beatson, R. K.}{1982}{Monotone and convex approximation by splines: error estimates and a curve fitting algorithm}{SIAM Journal on Numerical Analysis}{19(6):1278--1285}

%% Proves existence of splines that maintain monotonicity and convexity while having fixed continuity and order.
\refj{Costantini, P.}{1986}{On monotone and convex spline interpolation}{Mathematics of Computation}{46(173):203--214}

\refj{Cravero, I., C. Manni}{2003}{Shape-preserving interpolants with high smoothness}{Journal of computational and applied mathematics}{157, 383--405}

\refj{Delbourgo, R., Gregory,  J. A.}{1983}{$C^2$ rational quadratic spline interpolation to monotonic data}{IMA J. Numer. Anal.}{3, 141--152}

\refj{Delbourgo, R.}{1993}{Accurate $C^2$ rational interpolations in tension}{SIAM J. Numer. Anal.}{30, 595--607}

\refj{DeVore, R. A.}{1977}{Monotone approximation by splines}{SIAM J. Math. Anal.}{8, 891-905}

\refj{DeVore, R. A.}{1977}{Monotone approximation by polynomials}{SIAM J. Math. Anal.}{8, 906-921}

\refj{Dougherty, R. L., Edelman, A., Hyman, J. M.}{1989}{Nonnegativity-, monotonicity- convexity-preserving cubic and quintic Hermite interpolation}{Math. Comp.}{52, 471--494}

\refj{Gregory, J. A.,Delbourgo,  R.}{1982}{Piecewise rational quadratic interpolation to monotonic data}{IMA J. Numer. Anal.}{2, 123--130}

\refj{Fiorot, J. C., Tabka, J.}{1991}{Shape-preserving $C^2$ cubic polynomial interpolating splines}{Math. Comp.}{57, 291--298}

\refj{Han, X.}{2018}{Shape-preserving piecewise rational interpolation with higher order continuity}{Applied Mathematics and Computation}{337, 1-13}

\refj{Huynh, H. T.}{1993}{Accurate monotone cubic interpolation}{SIAM J. Numer. Anal.}{30, 57--100}

\refj{Kvasov, B. I.}{2014}{Monotone and convex interpolation by weighted quadratic splines}{Adv. Comput. Math.}{40, 91-116}

\refj{Manni, C., Sablonni\`ere, P.}{1997}{Monotone interpolation of order 3 by $C^2$ cubic splines}{IMA J. Numer.Anal.}{17, 305--320}

\refj{Manni, C.}{2001}{On shape preserving $C^2$ Hermite interpolation}{BIT Numerical Mathematics}{41, 127--148}

\refj{Pruess, S.}{1993}{Shape preserving $C^2$ cubic spline interpolation}{IMA J. Numer. Anal.}{13, 493--507}

\refj{Zhu, Y.,Han, X.}{2015}{$C^2$ rational quartic interpolation spline with local shape preserving property}{Appl. Math. Lett.}{46, 57-63}

\refj{Zhu, Y.,Han, X.}{2015}{Shape preserving $C^2$ rational quartic interpolation spline with two parameters}{International Journal of Computer Mathematics}{92, 2160-2177}
